### 2015-02-17 paper_40_mpi.tex
working on the end of chapter 4

        \subsubsection{OVERALL MPI SCORE}
            One complete overall score cannot be successful without including 
            information from various aspects of the software development 
            organization.  Therefore, the previous results
            are combined to provide one overall score.
            \[
                MPI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]

@@

    \subsection{IMPORTANCE OF MPI}

        Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
        areas and 3 important questions for software
        analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
        each focus area.  
        As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does provide
        any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
        the focus areas.

        \begin{longtable}{p{3cm}p{11cm}}
            % pairs: absolute number (percentage)

            \toprule%
             \centering%
             {\bfseries Focus Area}
             & {\bfseries Why MPI?} \\

@@

>>>>

        \subsubsection{OVERALL MPI SCORE}
            In order to accomplish the single number score that MPI requires,
            the 5 element scores must be combined. The combination of the scores
            is a weighted average.  The weights can be set based upon the 
            priority of the SDO.  Thus, the overall MPI score is calculated as below.

            \[
                MPI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]

    \subsection{CORRELATIONS IN MPI}
        It is possible that 2 or more of the 5 elements of MPI will be correlated.  This means that
        one of the elements can be predicted based upon the values of the other elements.  Although
        it is possible for correlation to occur between any of the elements, the satisfaction element
        is an obvious element which deserves attention due to the human involvement of the surveys. 
        If a schedule is missed or an important requirement dropped, that could have a large negative
        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
        possible that a decrease in quality could result in unexpected downtime which could have a
        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
        to missing functionality.

        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
        check for correlations after determining element and overall MPI scores.  
        If correlation is determined, the element should not be dropped but rather be weighted less than
        the other elements.  This technique keeps the most data available but lessens the importance of
        the correlated element.

@@

    \subsection{MPI COMPARED}

        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}

            Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
            areas  for software
            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
            each focus area.  
            As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does not provide
            any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
            the focus areas.

            \begin{longtable}{p{3cm}p{11cm}}
                \toprule%
                 \centering%
                 {\bfseries Focus Area}
                 & {\bfseries Why MPI?} \\

@@

        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how MPI addresses that specific question.  It is clear
            that MPI addresses the questions.  MPI is a beneficial technique of software
            analytics when applied to software development organizations.
